TBD

### 2019-02-06 inverse_problems/inverse_problems.tex
update of Poisson section

\paragraph{Poisson model.}

We consider the following observation model. $X = (X[0],\dots,X[L-1])$ is a random vector of length $L$, drawn from some fixed distribution. For fixed $n$, we observe a random vector $Y$ of length $n+L$, generated as follows. Points are chosen in $\{1,\dots,n\}$ according to a Poisson process with parameter $\gamma n$. For each point $i$ that is chosen from $1$ to $n$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.

@@

\section{Autocorrelation analysis} \label{sec:AC_analysis}

For a signal $z\in \R^m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
\begin{equation}
a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
\label{eq:ac_general}
\end{equation}
where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
Explicitly, the first-, second- and third-order autocorrelations are given by: 
\begin{align} 
a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell],\\
a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2].  \nonumber \label{eq:ac_special}
\end{align}
The autocorrelation functions have symmetries. Specifically, $$a_z^2[\ell] = a_z^2[-\ell],$$ and
$$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
$$
For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).

>>>>

\paragraph{Poisson model with a stochastic signal.}

The models we described so far assume a well-separated support and a deterministic signal. This models can be extended to stochastic signals and the separation condition can be alleviated by assuming a Poisson process. 
We consider the following observation model. Let $X =\RL$ be a random vector drawn from some fixed distribution. We observe a random vector $Y\in\R^{N-L+1}$ generated as follows. Points are chosen in $\{1,\dots,N-L=1\}$ according to a Poisson process with parameter $\gamma N$. The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.

@@

\section{Autocorrelation analysis} \label{sec:AC_analysis}
\TODO{Could be written for a random signal and then particularized to the homogeneous and heterogeneous cases.}
For a signal $z\in \R^m$, the autocorrelation of order $q = 1, 2, \ldots$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
\begin{equation}
a_z^q[\ell_1,\ldots,\ell_{q-1}]   = \frac{1}{m} \sum_{i=-\infty}^{\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
\label{eq:ac_general}
\end{equation}
where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
Explicitly, the first-, second- and third-order autocorrelations are given by: 
\begin{align} 
a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell],\\
a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2].  \nonumber \label{eq:ac_special}
\end{align}
The autocorrelation functions have symmetries. Specifically, $$a_z^2[\ell] = a_z^2[-\ell],$$ and
$$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
$$
For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
